\LARGE \bf Informed sampling by Markov Chain Monte Carlo methods

### 2017-02-24 paper.tex
note

In this paper, we suggest an alternative approach to produce samples in the informed set \Cinf for a wide range of settings.
\textbf{
Our main insight is to recast this problem of sampling uniformly within a level set of an implicit function.
This recasting enables us to apply Monte Carlo sampling methods, used very effectively in the optimization community, to solve our problem.
}
%
%\textbf{Our main insight is to formulate the problem as the problem of sampling uniformly below a level set of an implicit function and then apply optimization and statistical tools.}
\os{do we really care about uniformity?}
Specifically, our approach consists of two stages:
in the first, a random sample $x \in \calX$ is retracted to the boundary of~$\Cinf$ by running a root-finding algorithm;
in the second stage, this retracted sample~$\tilde{x}$ is used to seed a Monte Carlo sampling chain which allows us to  produce samples that (approximately) cover~$\Cinf$  uniformly.

@@

\subsection{Markov Chain Monte Carlo (MCMC)}
\label{subsec:mcmc}
\os{This section puts a lot of emphasis on HMC. If we end up choosing an alternative method, we should change the relevant weight}

Monte Carlo simulation is a general sampling framework widely used in various domains such as
statistical machine learning~\cite{M97},
motion tracking~\cite{KBD04}, 
data regression~\cite{TL11} and 
state estimation~\cite{ASC13}.
Roughly speaking, Monte Carlo simulation repeatedly samples a domain at random to approximate some value or function.
One specific domain where Monte Carlo simulation is used which is of specific interest to us is generating draws from a desired distribution which is hard to sample directly.

@@

>>>>

In this paper, we suggest an alternative approach to produce samples in the informed set \Cinf for a wide range of settings.
\textbf{
Our main insight is to recast this problem of sampling uniformly within a level set of an implicit function.
This recasting enables us to apply Monte Carlo sampling methods, used very effectively in the optimization community, to solve our problem.
}
%
%\textbf{Our main insight is to formulate the problem as the problem of sampling uniformly below a level set of an implicit function and then apply optimization and statistical tools.}
\os{do we really care about uniformity?}
\dy{Is it fair to say that uniformity guarantee each state has equal opportunity of being selected?}
Specifically, our approach consists of two stages:
in the first, a random sample $x \in \calX$ is retracted to the boundary of~$\Cinf$ by running a root-finding algorithm;
in the second stage, this retracted sample~$\tilde{x}$ is used to seed a Monte Carlo sampling chain which allows us to  produce samples that (approximately) cover~$\Cinf$  uniformly.

@@

\subsection{Markov Chain Monte Carlo (MCMC)}
\label{subsec:mcmc}
\os{This section puts a lot of emphasis on HMC. If we end up choosing an alternative method, we should change the relevant weight}
Monte Carlo simulation is a general sampling framework widely used in various domains such as
statistical machine learning~\cite{M97},
motion tracking~\cite{KBD04}, 
data regression~\cite{TL11} and 
state estimation~\cite{ASC13}.
Roughly speaking, Monte Carlo simulation repeatedly samples a domain at random to approximate some value or function.
One specific domain where Monte Carlo simulation is used which is of specific interest to us is generating draws from a desired distribution which is hard to sample directly.

@@

\dy{should the ``return'' in Algorithm 1 \ref{alg:mcmc_informed_sampling} be ``yield"?}
